---
title: "final project"
author: "yaru peng"
date: "5/5/2018"
output: ioslides_presentation
---
## About & Methodology
This research project aims to use twitter collected data from the following model: AdrianaLima, MarthaHunt, bellahadid, GiGiHadid, and KendallJenner. 

Using the data we will look at:
- the frequency of hashtag of model
- model post of the past month
- Comparing the ratio of follower to friends of these model 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
#install.packages("rtweet")
library(rtweet)
library(ggplot2)
library(tidytext)
library(tidyverse)
library(plotly)
library(readr)

  # Change the next four lines based on your own consumer_key, consume_secret, access_token, and access_secret. 
consumer_key <- "5Xtc6aCLL74G8bzSq6DLdzT5K"
consumer_secret <- "H2sle8DmuoHi1K7JYFpinOn4Y7wl2oUnT3j7Il3OXZWvkkhVcI"
access_token <- "992830297036144640-m6N0sExVoiyKMBOI3WURG1Pim2pEwBd"
access_secret <- "YuTocZ2LBK7c46EwuWe64Dyy5uwjtxTB5kfYYcbN4VEaq"

createTokenNoBrowser<- function(appName, consumerKey, consumerSecret, 
                                  accessToken, accessTokenSecret) {
  app <- httr::oauth_app(appName, consumerKey, consumerSecret)
  params <- list(as_header = TRUE)
  credentials <- list(oauth_token = accessToken, 
                      oauth_token_secret = accessTokenSecret)
  token <- httr::Token1.0$new(endpoint = NULL, params = params, 
                                     app = app, credentials = credentials)
  return(token)
}

token <- createTokenNoBrowser("ma415 -finalproject",consumer_key, consumer_secret, access_token, access_secret)
```


## Adriana Lima Frequency chart
```{r, message= FALSE}
adriana <- search_tweets("#adrianalima", n = 1000, include_rts = FALSE,token = token)

ts_plot(adriana, "3 hours") +
  ggplot2::theme_minimal() +
  ggplot2::theme(plot.title = ggplot2::element_text(face = "bold")) +
  ggplot2::labs(
    x = NULL, y = NULL,
    title = "Frequency of #adrianalima Twitter statuses from past month",
    subtitle = "Twitter status (tweet) counts aggregated using three-hour intervals",
    caption = "\nSource: Data collected from Twitter's REST API via rtweet"
  )
```


## Martha Hunt Frequency chart
```{r, message=FALSE}
martha <- search_tweets("#marthahunt", n = 1000, include_rts = FALSE,token = token)

ts_plot(martha, "3 hours") +
  ggplot2::theme_minimal() +
  ggplot2::theme(plot.title = ggplot2::element_text(face = "bold")) +
  ggplot2::labs(
    x = NULL, y = NULL,
    title = "Frequency of #marthahunt Twitter statuses from past month",
    subtitle = "Twitter status (tweet) counts aggregated using three-hour intervals",
    caption = "\nSource: Data collected from Twitter's REST API via rtweet"
  )
```



## Bellahadid Frequency Chart
```{r, message=FALSE}
bella <- search_tweets("#bellahadid", n = 1000, include_rts = FALSE,token = token)

ts_plot(bella, "3 hours") +
  ggplot2::theme_minimal() +
  ggplot2::theme(plot.title = ggplot2::element_text(face = "bold")) +
  ggplot2::labs(
    x = NULL, y = NULL,
    title = "Frequency of #bellahadid Twitter statuses from past month",
    subtitle = "Twitter status (tweet) counts aggregated using three-hour intervals",
    caption = "\nSource: Data collected from Twitter's REST API via rtweet"
  )
```


## Gigi Haldid Frequency Chart
```{r, message=FALSE}
gigi <- search_tweets("#gigihadid", n = 1000, include_rts = FALSE,token = token)

ts_plot(gigi, "3 hours") +
  ggplot2::theme_minimal() +
  ggplot2::theme(plot.title = ggplot2::element_text(face = "bold")) +
  ggplot2::labs(
    x = NULL, y = NULL,
    title = "Frequency of #gigihadid Twitter statuses from past month",
    subtitle = "Twitter status (tweet) counts aggregated using three-hour intervals",
    caption = "\nSource: Data collected from Twitter's REST API via rtweet"
  )
```

## Kendall Jenner Frequency Chart 
```{r, message=FALSE}
kendall <- search_tweets("#kendalljenner", n = 1000, include_rts = FALSE,token = token)

ts_plot(kendall, "3 hours") +
  ggplot2::theme_minimal() +
  ggplot2::theme(plot.title = ggplot2::element_text(face = "bold")) +
  ggplot2::labs(
    x = NULL, y = NULL,
    title = "Frequency of #kendalljenner Twitter statuses from past month",
    subtitle = "Twitter status (tweet) counts aggregated using three-hour intervals",
    caption = "\nSource: Data collected from Twitter's REST API via rtweet"
  )
```

## Observations

Looking at charts, we often see there being sudden peaks in the number of hashtags used on twitter. If we google those dates, it is often seen that the model was doing photoshot or attending an event that appeared on the news. 

## Model's Historical Post over past month 1
```{r, message=FALSE, warning=FALSE}
tmls <- get_timeline(c("AdrianaLima", "MarthaHunt","bellahadid","GiGiHadid","KendallJenner"), n=1000, token = token)
tmls %>%
  dplyr::filter(created_at > "2017-05-05") %>%
  dplyr::group_by(screen_name) %>%
  ts_plot("days", trim = 1L) +
  ggplot2::geom_point() +
  ggplot2::theme_minimal() +
  ggplot2::theme(
    legend.title = ggplot2::element_blank(),
    legend.position = "bottom",
    plot.title = ggplot2::element_text(face = "bold")) +
  ggplot2::labs(
    x = NULL, y = NULL,
    title = "Frequency of Twitter statuses posted by Models",
    subtitle = "Twitter status (tweet) counts aggregated by day from June-April 2018",
    caption = "\nSource: Data collected from Twitter's REST API via rtweet"
  )
```

## Observations 2

From the frequency of post, we can see that most post peaks correlates to the photoshot and events from the hashtag charts. Though except for one exception as clearly see as outlier (Martha Hunt's tweet explosion around November 2017) - This is when Martha Hunt attended the VS show and tweeted from behind the screen non-stop.


## Follower compared to friends table {.smaller}
```{r}
user <- lookup_users(c("AdrianaLima", "MarthaHunt","bellahadid","GiGiHadid","KendallJenner"), token = token)

ff.table <- rbind(user$followers_count,user$friends_count)
colnames(ff.table) <- c("AdrianaLima", "MarthaHunt","bellahadid","GiGiHadid","KendallJenner")
row.names(ff.table) <- c("follower count", "friends count")

ff.table
```
From the table, we can see a small inverse relationship of number of friends to followers.Meaning that the more famous the model becomes, the less people they tend to follow.
